---
title: "p8105_hw6_scl2160"
author: "Sam Loewen"
date: "11/18/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(modelr)
library(mgcv)
library(purrr)
```

# Problem 1

Cleaning data:

```{r}
bw = read.csv("./data/birthweight.csv") %>% 
  janitor::clean_names() %>% 
  mutate(babysex = as.factor(babysex),
         frace = as.factor(frace),
         malform = as.factor(malform),
         mrace = as.factor(mrace),
         menarche = ifelse(menarche == 0, "", menarche),
         fincome = as.numeric(ifelse(fincome == 0, "", fincome)),
         wtgain = as.numeric(ifelse(wtgain < 0, "", wtgain)),
         menarche = as.numeric(menarche))
```

I wanted to see the effect of income and race on birthweight, in the the absense of medical/health/physical indicators. For that reason I chose income, father's race, and mother's race.

## Plotting model one

```{r}
model_1 = lm(bwt ~ frace + mrace + fincome + frace*fincome + mrace*fincome, data = bw)

bw %>% 
  add_predictions(model_1) %>% 
  add_residuals(model_1) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point()+
 geom_line(aes(y = pred), color = "orange") +
    labs(
    title = "Predicted birthweight vs residuals",
    x = "predicted birthweight",
    y = "residuals"
  )
```

models 2 and 3:

```{r}
model_2 = lm(bwt ~ blength + gaweeks, data = bw)

model_3 = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = bw)
```


## Testing model fits

```{r}
rmse(model_1, bw)
rmse(model_2, bw)
rmse(model_3, bw)
```

```{r}
cv_df = 
  crossv_mc(bw, 100) 

cv_df = 
  cv_df %>% 
  mutate(model_1 = map(train, ~lm(bwt ~ fincome + mrace + frace, data = bw)), 
         model_2 = map(train, ~lm(bwt ~ blength + gaweeks, data = bw)),
         model_3 = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex, data = bw))) %>% 
  mutate(rmse_1 = map2_dbl(model_1, test, ~rmse(mode = .x, data = .y)),
         rmse_2 = map2_dbl(model_2, test, ~rmse(mode = .x, data = .y)),
         rmse_3 = map2_dbl(model_3, test, ~rmse(mode = .x, data = .y)))

cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_boxplot()

```

Model 3 is the best!

# Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

model:

```{r}
lm(tmax ~ tmin, data = weather_df) %>% 
  broom::tidy()
```

bootstrapping:

Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities. Plot the distribution of your estimates, and describe these in words.

Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r^2 and log(β^0∗β^1).

distribution of log(β^0∗β^1:

```{r}
weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    result = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(result) %>% 
  ggplot(aes(x = estimate)) + geom_density()
```

distribution of r^2:

```{r}
weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    result = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(result) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```

confidence interval of log(β^0∗β^1:

```{r}
weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    result = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(result) %>% 
  group_by(.id) %>% 
  summarize(log_coef = sum(log(estimate))) %>% 
  summarize(low_int = quantile(log_coef, 0.025), up_int = quantile(log_coef, .975))
```

confidence interval of r^2:

```{r}
weather_df %>% 
  modelr::bootstrap(n = 5000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x)),
    result = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(result) %>% 
  summarize(low_int = quantile(r.squared, 0.025), up_int = quantile(r.squared, .975))
```



